Conservation of interaction partners between related plants varies widely across communities and between plant families.

### 2019-06-11 manuscript/phylogenetic_signal_manuscript.tex
some DBS edits and comments

    \item We introduce a novel approach with which to quantify
          overlap of interaction
          partners for each pair of plants in 59 pollination and 11 herbivory
          networks.  We then tested for relationships between phylogenetic 
          distance and overlap within each network, and whether these 
          relationships varied with the composition of the plant community.
          Finally, we tested for different relationships within well-represented
          plant families.

@@

    \item The variety of relationships between phylogenetic distance and
          interaction partners in different plant families likely
          reflects a variety of ecological and evolutionary processes. To 
          understand the distribution of interactions within a community, 
          it is therefore important to consider factors affecting particular 
          plant families.

@@

@@

  If attractive and/or defensive traits are heritable,
  then we can reasonably expect that related plants will have similar 
  patterns of interactions with animals, especially if there is some selection in either group to avoid competition or the number of potential partners is limited~\citep{Schemske1999,Ponisio2017}. That is, there may be \emph{phylogenetic signal} in plants' interactions such that closely-related plants may tend to have similar interaction partners.
  Recent studies that have investigated this question at the level of whole
  communities, however, have yielded mixed results~\citep{Rezende2007a,Gomez2010,Rohr2014a,Fontaine2015,Lind2015,Ibanez2016,Bergamini2017,Sydenham2017,Volf2017,Hutchinson2017}.
  In particular, significant phylogenetic signal in plants' sets of interaction partners tends to be rare in empirical networks (\citealp{Rezende2007a,Lind2015,Ibanez2016}; but see~\citealp{Elias2013,Fontaine2015,Hutchinson2017}). Significant degrees of phylogentic signal and/or coevolution may also lead to only small differences in network structure, adding to the difficulty of understanding patterns in species' interaction partners~\citep{Ponisio2017}.
  Further, the plant and animal components of networks can show different degrees of phylogenetic conservation of interaction partners. In mutualistic networks, animals often show a stronger phylogenetic signal in their partners than plants~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015,Fontaine2015} (but see~\citep{Rafferty2013} for a counterexample). In antagonistic networks, however, actively-foraging consumers tend to show less phylogenetic signal than their prey~\citep{Ives2006,Cagnolo2011,Naisbit2011,Fontaine2015}. Thus, it is not straightforward to assume that interactions will be similar among related species. [[GVDR was skeptical of a similar point in the previous draft - less contentious now?]]
  % Further, plants' roles [[how defined?]] within networks tend to be less phylogenetically constrained than those of 
  % animals~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015}. [[GVDR is skeptical of this - check partiteness, size, type of role and add more detail to support.]] % I doubt this is really important, probably more trouble than it's worth.

@@

  [[Trying to emphasize the family-wise part as a point of difference from Fontaine \& Thebault, even though our results weren't the most exciting.]]
  Here we investigate how overlap in interaction partners between 
  pairs of plants (henceforth ``niche overlap'') varies over 
  phylogenetic distance and how this differs between plant families. 
  Whereas previous 
  studies have focused on the presence or absence of phylogenetic
  signal across entire networks, we take a pairwise perspective in
  order to ontain a more detailed picture of how plant phylogeny
  relates to network structure. Specifically,
  we test whether niche overlap decreases over increasing phylogenetic
  distance in a large dataset of pollination and herbivory networks, 
  whether the plant family composition of a community affects the
  relationship between niche overlap and phylogenetic distance in that 
  community, and whether the relationship between niche overlap and 
  phylogenetic distance differs across plant families.

@@

  We studied tested for phylogenetic signal in niche overlap within a 
  set of 59 pollination and 11 herbivory networks. These networks span 
  a range of biomes (desert to scrub forest to grassland) and 
  countries (Sweden to Australia). The herbivory networks included a 
  variety of types of herbivores but were dominated by insects 
  consuming leaves. To ensure that we were analysing interactions 
  influenced by similar sets of traits across networks, we restricted 
  our herbivory networks to insects consuming leaves and excluded 
  sap-sucking, leaf-mining, and galling insects as well as seed 
  predators and xylophagous insects; all of these interactions involve 
  different plant tissues and means of feeding than leaf consumption 
  and so may be influenced by different plant and insect traits. 
  Specifically, we removed any non-leaf consuming insects and any 
  plants which had no interaction partners after removing other types  
  of herbivores. The adjusted networks range in size between 19 and 
  997 total species (mean=162, median=97) with between 8 and 132 
  plant species (mean=39.1, median=29.5). See \emph{Table S1, 
  Supporting information 1} for details on the original sources of all 
  networks.

@@

  We then estimated phylogenetic distances between species. To accomplish 
  this, we constructed a phylogenetic tree for our dataset based on a dated
  `mega-tree' of angiosperms~\citep{Zanne2014}. Some species were not included
  in the angiosperm mega-tree (largely ferns and tree ferns). For angiosperms,
  a sister taxon was identified using~\citet{APW} and the species added manually.
  Ferns, tree ferns, and a single club moss were added to the base of the tree.
  This means that closely-related non-angiosperm species appear to have very long 
  phylogenetic distances between them. For this reason, we excluded comparisons 
  between pairs of non-angiosperms from our analyses. As only two networks (both 
  herbivory networks) included more than one such species and non-angiosperms
  were always a small minority of any network, we do not 
  believe that omitting these comparisons has greatly affected our results.
  To obtain trees for each network, we 
  pruned the dated mega-tree to include only species in that network.

@@

  We calculated niche overlap for each pair of species within a community 
  using a Jaccard index to describe the number of shared interaction 
  partners, augmented with the number of interaction partners which were 
  not shared. The Jaccard index $J_{ij}$ describes the proportion of 
  shared interaction partners for for species $i$ and $j$ and is defined as:

  \begin{equation}
    J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
  \end{equation}

  where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
  species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
  \emph{partners} for species $i$ and $j$ respectively. We wished to give more 
  weight to species sharing a large number of interaction partners as well as 
  those sharing a large proportion (i.e., to emphasize pairs of generalists 
  sharing most of their interaction partners over specialists sharing a single 
  interaction partner). We therefore recorded, for each species, the number of 
  shared interaction partners $M_{ij}$ and the number of interaction partners 
  for each species pair that were not shared 
  ($U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$). Instead of a single index $J_{ij}$ 
  we therefore keep track of the information needed to compute
  niche between species $i$ and $j$ as a tuple: ($M_{ij}$, $U_{ij}$).

@@

  We modelled the relationship between niche overlap and phylogenetic 
  distance using a logistic regression. We used both the numbers of shared 
  ($M_{ij}$) and non-shared ($U_{ij}$) partners as dependent variables and 
  centred, scaled phylogenetic distance as the independent variable. This 
  approach is conceptually similar to modelling successes and failures in a 
  binomial-distributed process. Accordingly, we assumed a binomial 
  distribution for residuals and used a logit link function to model the 
  probability $\omega_{ij}$ of plants $i$ and $j$ sharing an interaction 
  partner. Regressions of niche overlap and phylogenetic distance within 
  each network were fit using the R~\citep{R} base function ``glm'' and 
  took the form

    \begin{equation}
      \omega_{ij} \propto \beta_{distance}\delta_{ij} ,
      \label{basic}
    \end{equation}

  where $\delta_{ij}$ is the phylogenetic distance between plants $i$ and 
  $j$. The fixed effect of distance in this regression, $\beta_{distance}$, 
  can be understood as the change in log odds of sharing an interaction 
  partner per million-year change in phylogenetic distance.

  These separate regressions avoid the potential for confounding the effects
  of different relationships in different networks. As we also wished to 
  evaluate the overall trend across networks, we fit an additional
  regression of niche overlap and phylogenetic distance across all network 
  types. As well as the fixed effect of phylogenetic distance, this 
  regression included fixed effects of network type (pollination or 
  herbivory) and the interaction between phylogenetic network type and 
  random intercepts and slopes per network. This expanded regression was fit
  using the R~\citep{R} function ``glmer'' from package 
  \emph{lme4}~\citep{lme4} and took the form

    \begin{equation}
      \omega_{ij} \propto \beta_{distance} \delta_{ij} + \beta_{pollination} I_{ij} + \beta_{distance:pollination} \delta_{ij} I_{ij} ,
    \end{equation}

  where $I_{ij}=1$ when plants $i$ and $j$ are drawn from a 
  pollination network and $I_{ij}=0$ otherwise and all other symbols 
  are as above. Note that we only compared pairs of plants taken from the 
  same network. The fixed effects $\beta_{pollination}$ and $\beta_{distance:pollination}$ 
  are the change in intercept and slope of the log odds of sharing an 
  interaction partner, respectively relative to the baseline of 
  herbivory networks.

@@

  This permutation approach also allows us to estimate type I and type II 
  error for our analysis. To do this, we created 500 permutations of each 
  permuted network and, again keeping the observed phylogenetic distances 
  between plant species, repeated our analyses. We can then determine the 
  number of permuted networks which appear to have significant 
  overlap-phylogenetic distance relationships relative to the permutations 
  of these permuted networks (type I error). Type II error can be determined
  from the distribution of p-values obtained when comparing the permuted 
  networks to permutations of the permuted networks. Although calculating 
  the exact type II error requires a specific alternative hypothesis, the 
  uniform distribution of p-values we obtained after permuting the permuted 
  networks means that the type II error would increase linearly as the 
  alternative hypothesis was set farther from zero. [[Is this cogent? Correct? If not, I think I will have to remove all reference to type II error and hope we don't get the same reviewer again. It may not be an issue since we've moved away from the motif-like measures.]]

  To test whether the relationship between phylogenetic distance and niche overlap depended on network size, we fit a general linear model for the slope of this relationship in the glm models against the number of plant pairs for which distances could be calculated (hereafter ``network size"), network type (again using herbivory networks as a baseline), and their interaction:

    \begin{equation}
      \beta_{distance} \propto \beta_{size} \eta_{N} + \beta_{pollination} I_N + \beta_{size:pollination} \eta_{N} I_N ,
    \end{equation}

  where $\eta_{N}$ is the number of plant pairs in network $N$ for which distances could be calculated, $I_N$ is an indicator equal to 1 if network $N$ is a pollination network and 0 otherewise.

@@

  Next, we examined the connection between our network-level observations
  and the plant families present in each community.
  Specifically, we tested the hypothesis that
  varying relationships between phylogenetic distance and
  pairwise niche overlap are due to the different distributions 
  of families across networks. We defined the relationship between
  phylogenetic distance and niche overlap as the change in 
  log odds of two plants in a given network sharing an interaction 
  partner per million years of divergence (i.e., the slope from the 
  regression of niche overlap against phylogenetic distance within
  a single network). We then related differences in this relationship
  to differences in the composition of the plant community in each
  network using a non-parametric permutational multi-variate 
  analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
  As we did not wish to inflate the perceived similarity between
  pairs of networks which did not include many of the same families,
  we used Bray-Curtis dissimilarity to define differences in plant
  community composition. Bray-Curtwis dissimilarity considers only
  those plant families which appear in at least one of a pair of
  networks~\citep{Anderson2001,Cirtwill2015}, ensuring that the
  shared absence of rare plant families will not make 
  two networks appear more similar than they actually are.

  Note that a PERMANOVA does not assume that the data are 
  normally distributed, but rather compares the pseudo-$F$ 
  statistic calculated from the observed data to a null 
  distribution obtained by permuting the raw data. As 
  pollination and herbivory networks might have different
  community composition, we stratified these permutations
  by network type. That is, the change in log odds for a pollination
  network could only be exchanged for that of another pollination
  network. Stratifying the permutations in this way ensures that 
  the null distribution used to calculate the $P$-value is not 
  biased by including combinations of changes in log odds and 
  community composition that would not occur because of inherent 
  differences in the two network types (e.g., \emph{Pinaceae} 
  only appeared in herbivory networks and should not be assigned 
  to pollination networks). We used 9999 such stratified permutations 
  to obtain the null distribution and obtain a $P$-value.

@@

    Comparing the results in the observed networks to those obtained after 
    permuting phylogenetic distances across pairs of plants, the observed 
    slope of the relationship between phylogenetic distance and interaction 
    partner overlap was always more extreme (i.e., always lesser or always 
    greater) than that obtained in the permuted networks (Fig.~\ref{obs_vs_random}).
    Observed networks with a negative relationship between phylogenetic distance 
    and overlap always had a more negative slope than that obtained from the 
    permuted networks, while the 10 networks with positive relationships 
    between phylogenetic distance and overlap always had more positive 
    relationships than the permuted networks. This suggests that even in 
    the networks with non-significant relationships between niche overlap 
    and phylogenetic distance, the association between niche overlap and 
    phylogenetic distance was not random. When the slopes of the permuted 
    networks were compared to those obtained from permutations of the 
    permuted networks, there was no relationship (\emph{Supporting 
    information 2}).

@@

    We were interested in whether the slope of the relationship between phylogenetic distance varied with community composition. In a PERMANOVA of slope against community composition, stratified by network type, we did not find a significant relationship between slope and community composition ($F_{1,68}$=1.06, $p$=0.493). Of the 200 families in our dataset, only 29 were represented by more than 20 species. Lumping all other families into an "other" category and repeating the PERMANOVA, we still did not find a significant relationship between slope and community composition ($F_{1,68}$=1.12, $p$=0.409). 
    % Also performed a CCA to see which fams had most positive/negative associations, but with non-sig results I don't think it's interesting.

@@

    Considering each family separately, the relationship between within-family niche overlap and phylogenetic distance varied widely in both pollination and herbivory networks. 
    For the families
    that were well represented in pollination networks, overlap decreased
    with increasing phylogenetic distance in 18 (Table~\ref{family_slopes_pp}).
    There was no significant relationship between overlap and phylogenetic distance in
    a further 15 plant families. Finally, the overlap between pairs of \emph{Polygonaceae}
    increased with increasing phylogenetic distance. 
    Of the seven plant families that were sufficiently well represented in herbivory 
    networks, overlap decreased with increasing phylogenetic distance in four 
    (Table~\ref{family_slopes_ph}; Fig.~\ref{within_family_regression}). Two
    families did not show significant relationships between phylogenetic distance and overlap,
    and in one family, \emph{Fabaceae}, overlap of interaction partners increased with 
    increasing phylogenetic distance.

@@

@@

  We found broad support for the hypothesis that more
  closely-related pairs of plants have a higher degree
  of niche overlap. Using a novel method which considers
  all pairs of plants together, 
  the probability of two plants sharing the same animal 
  interaction partners generally decreased with increasing 
  phylogenetic distance. Considering networks separately,
  $\approx$56\%  of the pollination and $\approx$64\% of the 
  herbivory networks exhibited the expected trend of decreasing 
  overlap with increasing distance. This variation between networks
  echoes earlier studies (e.g.,~\citep{Fontaine2015,Hutchinson2017})
  which also found broad evidence for phylogenetic conservation
  of interaction partners despite variation between particular 
  networks. 
  % The lack of a relationship between phylogenetic
  % distance and interaction partner overlap in many networks 
  % could have several explanations. First, our dataset included
  % many extreme specialists, especially among the pollination 
  % networks. These species interact with only one plant and
  % therefore weaken any signal of interaction partner overlap.

@@

  For those families which were well-represented in both pollination
  and herbivory networks, we can also contrast the 
  trends in the two network types. While \emph{Asteraceae} showed the
  expected decrease in interaction partner overlap with increasing
  phylogenetic distance, the other families showed different trends in
  different network types. This may indicate that one type of interaction
  places greater constraints upon these families than the other. Plants
  may not be able to respond to selection on both types of interaction
  simultaneously because traits affecting pollination can also affect herbivory, and vice
  versa~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
  Associations with pollinators and herbivores may also be constrained by the
  larger structure of the community. In one recent study, plants which are 
  visited by many pollinators are also consumed by many herbivores~\citep{Sauve2016}.
  This may be because pairing antagonistic and mutualistic interactions
  balances the indirect effects of these interactions, leading to a
  more stable community~\citep{Sauve2014}. As more networks describing 
  pollination and herbivory in the same community become available, it 
  will be interesting to test this hypothesis more thoroughly.

@@

  \begin{figure}[!h]
    \begin{center}
      \centerline{\includegraphics*[width=.75\textwidth]{Figures/dataplots/scaled_regression_lines_full_color.eps}}
    \end{center}
     \caption{Results of a mixed-effects logistic regression of pairwise niche overlap
     against phylogenetic distance for plants in 11
     herbivory networks (top; green) and 59 pollination
     networks (bottom; purple). In both network types, the probability of a pair of plants
     sharing an interaction partner increased with increasing phylogenetic distance (thick,
     dark lines). There was substantial variation among networks (thin, pale lines) of both types. The slope of the regression for each network was significantly more extreme than that obtained from 999 permutatations of that network (slopes obtained from the permuted networks ranged between -1.34$\times10^{-12}$ and 9.19$\times10*{-13}$).}
    \label{within_network_regression} 
  \end{figure}

>>>>

    \item We introduce a novel approach with which to quantify
          overlap of interaction
          partners for each pair of plants in 59 pollination and 11 herbivory
          networks.  We then tested for relationships between phylogenetic 
          distance and partner overlap within each network, and whether these 
          relationships varied with the composition of the plant community.
          Finally, we tested for different relationships within well-represented
          plant families.

@@

    \item The variety of relationships between phylogenetic distance and
          interaction partners in different plant families likely
          reflects a comparable variety of ecological and evolutionary processes. To 
          understand the distribution of interactions within a community, 
          it is therefore important to consider factors affecting particular 
          plant families.

@@

\textbf{DBS: }

@@

  If attractive and/or defensive traits are heritable,
  then we can reasonably expect that related plants will have similar 
  patterns of interactions with animals, especially if there is some selection in either group to avoid competition or the number of potential partners is limited~\citep{Schemske1999,Ponisio2017}. That is, there may be \emph{phylogenetic signal} in plants' interactions such that closely-related plants may tend to have similar interaction partners.
  Recent studies that have investigated this question at the level of whole
  communities, however, have yielded mixed results~\citep{Rezende2007a,Gomez2010,Rohr2014a,Fontaine2015,Lind2015,Ibanez2016,Bergamini2017,Sydenham2017,Volf2017,Hutchinson2017}.
  In particular, significant phylogenetic signal in plants' sets of interaction partners tends to be rare in empirical networks (\citealp{Rezende2007a,Lind2015,Ibanez2016}; but see~\citealp{Elias2013,Fontaine2015,Hutchinson2017}). Significant degrees of phylogentic signal and/or coevolution may also lead to only small differences in network structure, adding to the difficulty of understanding patterns in species' interaction partners~\citep{Ponisio2017}.
  Further, the plant and animal components of networks can show different degrees of phylogenetic conservation of interaction partners. In mutualistic networks, animals often show a stronger phylogenetic signal in their partners than do plants~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015,Fontaine2015} (but see~\citep{Rafferty2013} for a counterexample). In antagonistic networks, however, actively-foraging consumers tend to show less phylogenetic signal than their prey~\citep{Ives2006,Cagnolo2011,Naisbit2011,Fontaine2015}. Thus, it is not straightforward to assume that interactions will always be similar among related species. [[GVDR was skeptical of a similar point in the previous draft - less contentious now?]]
  % Further, plants' roles [[how defined?]] within networks tend to be less phylogenetically constrained than those of 
  % animals~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015}. [[GVDR is skeptical of this - check partiteness, size, type of role and add more detail to support.]] % I doubt this is really important, probably more trouble than it's worth.

@@

  [[Trying to emphasize the family-wise part as a point of difference from Fontaine \& Thebault, even though our results weren't the most exciting.]]
  Here we investigate how overlap in interaction partners between 
  pairs of plants (henceforth ``niche overlap'') varies over 
  phylogenetic distance and how this differs between plant families. 
  Whereas previous 
  studies have focused on the presence or absence of phylogenetic
  signal across entire networks, we take a pairwise perspective in
  order to obtain a more detailed picture of how plant phylogeny
  relates to network structure. Specifically,
  we test whether niche overlap decreases over increasing phylogenetic
  distance in a large dataset of pollination and herbivory networks, 
  whether the plant family composition of a community affects the
  relationship between niche overlap and phylogenetic distance in that 
  community, and whether the relationship between niche overlap and 
  phylogenetic distance differs systematically across plant families.

@@

  We tested for phylogenetic signal in niche overlap within a 
  set of 59 pollination and 11 herbivory networks. These networks span 
  a range of biomes (desert to scrub forest to grassland) and 
  countries (Sweden to Australia). The herbivory networks included a 
  variety of types of herbivores but were dominated by insects 
  consuming leaves. To ensure that we were analysing interactions 
  influenced by similar sets of traits across networks, we restricted 
  our herbivory networks to insects consuming leaves and excluded 
  sap-sucking, leaf-mining, and galling insects as well as seed 
  predators and xylophagous insects; all of these interactions involve 
  different plant tissues and means of feeding than leaf consumption 
  and so may be influenced by different plant and insect traits. 
  Specifically, we removed any non-leaf consuming insects and any 
  plants which had no interaction partners after removing other types  
  of herbivores. The adjusted networks range in size between 19 and 
  997 total species (mean=162, median=97) with between 8 and 132 
  plant species (mean=39.1, median=29.5). See \emph{Table S1, 
  Supporting information 1} for details on the original sources of all 
  networks.

@@

  We then estimated phylogenetic distances between the remaining species. To accomplish 
  this, we constructed a phylogenetic tree for our dataset based on a dated
  `mega-tree' of angiosperms~\citep{Zanne2014}. Some species were not included
  in the angiosperm mega-tree (largely ferns and tree ferns). For angiosperms,
  a sister taxon was identified using~\citet{APW} and the species added manually.
  Ferns, tree ferns, and a single club moss were added to the base of the tree.
  This means that closely-related non-angiosperm species appear to have very long 
  phylogenetic distances between them. For this reason, we excluded comparisons 
  between pairs of non-angiosperms from our subsequent analyses. As only two networks (both 
  herbivory networks) included more than one such species and non-angiosperms
  were always a small minority of any network, we do not 
  believe that omitting these comparisons has greatly affected our results.
  To obtain trees for each network, we 
  pruned the dated mega-tree to include only species in that network.

@@

  We calculated niche overlap for each pair of species within a community 
  using a Jaccard index to describe the number of shared interaction 
  partners, augmented with the number of interaction partners which were 
  not shared. The Jaccard index $J_{ij}$ describes the proportion of 
  shared interaction partners for for species $i$ and $j$ and is defined as: 
%
  \begin{equation}
    J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
  \end{equation}
%
  where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
  species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
  \emph{partners} for species $i$ and $j$ respectively. We wished to give more 
  weight to species sharing a large number of interaction partners as well as 
  those sharing a large proportion (i.e., to emphasize pairs of generalists 
  sharing most of their interaction partners over specialists sharing a single 
  interaction partner). For each species pair, we therefore recorded the number of 
  shared interaction partners ($M_{ij}$) and the number of interaction partners 
  that were not shared 
  ($U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$). Instead of a single index $J_{ij}$, 
  we thus kept track of the full information needed to compute
  niche overlap between species $i$ and $j$ as a tuple: ($M_{ij}$, $U_{ij}$).

@@

  We modelled the relationship between niche overlap and phylogenetic 
  distance using a logistic regression. We used both the numbers of shared 
  ($M_{ij}$) and non-shared ($U_{ij}$) partners as dependent variables and 
  centred, scaled phylogenetic distance as the independent variable. This 
  approach is conceptually similar to modelling successes and failures in a 
  binomial-distributed process. Accordingly, we assumed a binomially-  distributed error structure and used a logit link function to model the 
  probability $\omega_{ij}$ of plants $i$ and $j$ sharing an interaction 
  partner. Regressions of niche overlap and phylogenetic distance within 
  each network were fit using the R~\citep{R} base function ``glm'' and 
  took the form
%
    \begin{equation}
      {\rm logit}\left(\omega_{ij}\right) \propto \beta_{distance}\delta_{ij} ,
      \label{basic}
    \end{equation}
%
  where $\delta_{ij}$ is the phylogenetic distance between plants $i$ and 
  $j$. The fixed effect of distance in this regression, $\beta_{distance}$, 
  can be understood as the change in log odds of sharing an interaction 
  partner per million-year change in phylogenetic distance.

  These separate regressions avoid the potential for confounding the effects
  of different relationships in different networks. As we also wished to 
  evaluate the overall trend across networks, we fit an additional
  regression of niche overlap and phylogenetic distance across all network 
  types. As well as the fixed effect of phylogenetic distance, this 
  regression included fixed effects of network type (pollination or 
  herbivory) and the interaction between phylogenetic network type and 
  random intercepts and slopes per network. This expanded regression was fit
  using the R~\citep{R} function ``glmer'' from package 
  \emph{lme4}~\citep{lme4} and took the form
%
    \begin{equation}
      {\rm logit}\left(\omega_{ij}\right) \propto \beta_{distance} \delta_{ij} + \beta_{pollination} I_{ij} + \beta_{distance:pollination} \delta_{ij} I_{ij} ,
    \end{equation}
%
  where $I_{ij}=1$ when plants $i$ and $j$ are drawn from a 
  pollination network and $I_{ij}=0$ otherwise and all other symbols 
  are as above. Note that we only compared pairs of plants taken from the 
  same network. The fixed effects $\beta_{pollination}$ and $\beta_{distance:pollination}$ 
  are the change in intercept and slope of the log odds of sharing an 
  interaction partner, respectively relative to the baseline of 
  herbivory networks.

@@

  This permutation approach also allows us to estimate type I and type II 
  error for our analysis. To do this, we created 500 permutations of each 
  permuted network and, again keeping the observed phylogenetic distances 
  between plant species, repeated our analyses. We can then determine the 
  number of permuted networks which appear to have significant 
  overlap-phylogenetic distance relationships relative to the permutations 
  of these permuted networks (type I error). Type II error can be determined
  from the distribution of p-values obtained when comparing the permuted 
  networks to permutations of the permuted networks. Although calculating 
  the exact type II error requires a specific alternative hypothesis, the 
  uniform distribution of p-values we obtained after permuting the permuted 
  networks means that the type II error would increase linearly as the 
  alternative hypothesis was set farther from zero.
  % [[Is this cogent? Correct? If not, I think I will have to remove all reference to type II error and hope we don't get the same reviewer again. It may not be an issue since we've moved away from the motif-like measures.]]
  % DBS: I think it's fine.

  To test whether the relationship between phylogenetic distance and niche overlap depended on network size, we fit a general linear model for the slope of this relationship inferred from the glm models against the number of plant pairs for which distances could be calculated (hereafter ``network size"), network type (again using herbivory networks as a baseline), and their interaction:
%
    \begin{equation}
      \beta_{distance} \propto \beta_{size} \eta_{N} + \beta_{pollination} I_N + \beta_{size:pollination} \eta_{N} I_N ,
    \end{equation}
%
  where $\eta_{N}$ is the number of plant pairs in network $N$ for which distances could be calculated, $I_N$ is an indicator equal to 1 if network $N$ is a pollination network and 0 otherewise.

@@

  Next, we examined the connection between our network-level observations
  and the plant families present in each community.
  Specifically, we tested the hypothesis that
  varying relationships between phylogenetic distance and
  pairwise niche overlap are due to the different distributions 
  of families across networks. We defined the relationship between
  phylogenetic distance and niche overlap as the change in 
  log odds of two plants in a given network sharing an interaction 
  partner per million years of divergence (i.e., the slope $\beta_{distance}$ from the 
  regression of niche overlap against phylogenetic distance within
  a single network). We then related differences in this relationship
  to differences in the composition of the plant community in each
  network using a non-parametric permutational multi-variate 
  analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
  As we did not wish to inflate the perceived similarity between
  pairs of networks which did not include many of the same families,
  we used Bray-Curtis dissimilarity to define differences in plant
  community composition. Bray-Curtis dissimilarity considers only
  those plant families which appear in at least one of a pair of
  networks~\citep{Anderson2001,Cirtwill2015}, ensuring that the
  shared absence of rare plant families will not make 
  two networks appear more similar than they actually are.

  Note that a PERMANOVA does not assume that the data are 
  normally distributed, but rather compares the pseudo-$F$ 
  statistic calculated from the observed data to a null 
  distribution obtained by permuting the raw data. As 
  pollination and herbivory networks might have different
  community composition, we stratified these permutations
  by network type. That is, the response variable of change in log odds for a pollination
  network could only be exchanged for that of another pollination
  network. Stratifying the permutations in this way ensures that 
  the null distribution used to calculate the $P$-value is not 
  biased by including combinations of changes in log odds and 
  community composition that would not occur because of inherent 
  differences in the two network types (e.g., \emph{Pinaceae} 
  only appeared in herbivory networks and should not be assigned 
  to pollination networks). We used 9999 such stratified permutations 
  to obtain the null distribution and obtain a $P$-value.

@@

    Comparing the results in the observed networks to those obtained after 
    permuting phylogenetic distances across pairs of plants, the observed 
    slope of the relationship between phylogenetic distance and interaction 
    partner overlap was always more extreme (i.e., always lesser or always 
    greater) than that obtained in the permuted networks (Fig.~\ref{obs_vs_random}).
    Observed networks with a negative relationship between phylogenetic distance 
    and overlap always had a more negative slope than that obtained from the 
    permuted networks, while the 10 networks with positive relationships 
    between phylogenetic distance and overlap always had more positive 
    relationships than the permuted networks. This suggests that even in 
    the networks with non-significant relationships, the association between niche overlap and 
    phylogenetic distance was not random. When the slopes of the permuted 
    networks were compared to those obtained from permutations of the 
    permuted networks, there was no relationship, which speaks to the robustness of our methodology (\emph{Supporting 
    information 2}).

@@

    We were interested in whether the slope of the relationship between phylogenetic distance varied with community composition. In a PERMANOVA of slope against community composition, stratified by network type, we did not find a significant relationship between slope and community composition ($F_{1,68}$=1.06, $p$=0.493). Of the 200 families in our dataset, only 29 were represented by more than 20 species. Lumping all other families into an ``other'' category and repeating the PERMANOVA, we still did not find a significant relationship between slope and community composition ($F_{1,68}$=1.12, $p$=0.409). 
    % Also performed a CCA to see which fams had most positive/negative associations, but with non-sig results I don't think it's interesting.

@@

    Considering each family separately, the relationship between within-family niche overlap and phylogenetic distance varied widely in both pollination and herbivory networks. 
    For the 47 families % DBS: Alyssa, please check this number!
    that were well represented in pollination networks, overlap decreased
    with increasing phylogenetic distance in 18 (Table~\ref{family_slopes_pp}).
    There was no significant relationship between overlap and phylogenetic distance in
    a further 15 plant families. Finally, the overlap between pairs of \emph{Polygonaceae}
    % DBS: According to the table, this should probably be Apiaceae and Poaceae. Please check.
    increased with increasing phylogenetic distance. 
    Of the seven plant families that were sufficiently well represented in herbivory 
    networks, overlap decreased with increasing phylogenetic distance in four 
    (Table~\ref{family_slopes_ph}; Fig.~\ref{within_family_regression}). Two
    families did not show significant relationships between phylogenetic distance and overlap,
    and in one family, \emph{Fabaceae}, overlap of interaction partners increased with 
    increasing phylogenetic distance.

@@

    % DBS: The section above seems like it would fit better in the Methods and then we just say nothing about these families.

@@

  We found broad support for the hypothesis that more
  closely-related pairs of plants have a higher degree
  of niche overlap. Using a novel method which considers
  all pairs of plants together, 
  the probability of two plants sharing the same animal 
  interaction partners generally decreased with increasing 
  phylogenetic distance. Considering networks separately,
  $\approx$56\%  of the pollination and $\approx$64\% of the 
  herbivory networks exhibited the expected trend of decreasing 
  overlap with increasing distance. This variation between networks
  echoes earlier studies \citep[e.g.,][]{Fontaine2015,Hutchinson2017}
  which also found broad evidence for phylogenetic conservation
  of interaction partners despite variation between particular 
  networks. 
  % The lack of a relationship between phylogenetic
  % distance and interaction partner overlap in many networks 
  % could have several explanations. First, our dataset included
  % many extreme specialists, especially among the pollination 
  % networks. These species interact with only one plant and
  % therefore weaken any signal of interaction partner overlap.

@@

  For those few families which were well-represented in \emph{both} pollination
  and herbivory networks, we can also contrast the 
  trends in the two network types. While \emph{Asteraceae} showed the
  expected decrease in interaction partner overlap with increasing
  phylogenetic distance, the other families showed different trends in
  different network types. This may indicate that one type of interaction
  places greater constraints upon these families than the other. Plants
  may not be able to respond to selection on both types of interaction
  simultaneously because traits affecting pollination can also affect herbivory, and vice
  versa~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
  Associations with pollinators and herbivores may also be constrained by the
  larger structure of the community. In one recent study, plants which are 
  visited by many pollinators are also consumed by many herbivores~\citep{Sauve2016}.
  This may be because pairing antagonistic and mutualistic interactions
  balances the indirect effects of these interactions, leading to a
  more stable community~\citep{Sauve2014}. As more networks describing 
  pollination and herbivory in the same community become available, it 
  will be interesting to test this hypothesis more thoroughly.

@@

  \begin{figure}[!h]
    \begin{center}
      \centerline{\includegraphics*[width=.75\textwidth]{Figures/dataplots/scaled_regression_lines_full_color.eps}}
    \end{center}
     \caption{Results of a mixed-effects logistic regression of pairwise niche overlap
     against phylogenetic distance for plants in 11
     herbivory networks (top; green) and 59 pollination
     networks (bottom; purple). In both network types, the probability of a pair of plants
     sharing an interaction partner increased with increasing phylogenetic distance (thick,
     dark lines). There was substantial variation among networks (thin, pale lines) of both types. The slope of the regression for each network was significantly more extreme than that obtained from 999 permutatations of that network (slopes obtained from the permuted networks ranged between -1.34$\times10^{-12}$ and 9.19$\times10^{-13}$).}
    \label{within_network_regression} 
  \end{figure}
